---
title: "Welcome and getting started"
description: |
  Material for onboarding new researchers at SDCA.
author:
    # Order alphabetical by last name
  - name: Daniel B. Ibsen
    affiliation: Steno Diabetes Center Aarhus, Denmark
  - name: Tinne Laurberg
    affiliation: Steno Diabetes Center Aarhus, Denmark
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r disclaimer, child="../../includes/disclaimer.Rmd"}
```

# Welcome!!

We have high ambitions at SDCA. We believe that people with diabetes can have a
good life. We will make a difference to all people with or at risk of getting
diabetes in Central Denmark Region.

As a new member of our research team, there is a lot of things you need learn
about the organization, the culture (both research and social) and a lot of
practical stuff. The page here is thought of as your initial entry point, where
you can get an overview. This is also an atlas for you to return to when you
need to look up specific information.

To get an introduction to the research team and this document you will be teamed
up with an experienced member from research. It is your supervisor's
responsibility to find you a "buddy." Please ask your supervisor if this is not
already in place.

Your buddy will walk you through the relevant tables below and give you an
overview of all the topics that you need to be aware of. The agenda for the
meeting is:

1. Introduce yourselves
2. Go through the table below
3. Take a tour around the research facility
4. Arrange follow-up talk

The purpose of the follow-up talk is to catch up on how you have settled in. If
you have any specific questions you can also ask them. As the final thing, you
and your buddy will evaluate the introduction. You will be given responsibility
to update this website if you have encountered  any information that was not up
to date and you should add any other information you would have liked the page
to contain. This is a very important step because it ensures that this material
is always current and helps the next new team member.

# General information

```{r generate-info-from-spreadsheet, echo=FALSE, results='asis'}
library(googlesheets4)
library(tidyr)
library(magrittr)
library(gt)
options(knitr.kable.NA = "")

# Don't need an access token to read in the sheet
gs4_deauth()

info_sheet <- read_sheet("1Be4YskAsAALO9GWmLmRFQhK-WuDo4ciKzqxa-0auM9M", range = "A1:C100") %>% 
    fill(Topic) %>% 
    na.omit()

for (topic in split(info_sheet, info_sheet$Topic)) {
    cat(paste0("\n\n## ", unique(topic$Topic), "\n\n"))
    
    gt(topic[-1]) %>% 
        opt_row_striping() %>% 
        tab_style(
            style = cell_text(weight = "bold"),
            locations = cells_column_labels()
        ) %>% 
        tab_options(table.width = pct(100)) %>% 
        print()
}
```

# PhD students

*table coming soon*
