---
title: "Contributing guidelines"
description: |
  Guidelines for contributing to the documents.
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(vembedr)
```

This document contains instructions for how to contribute to developing these
documents.

# Guiding principles

In order to ensure that we get the most from creating these documents and that
we don't spend more time on this than is necessary (given it is largely a
secondary task and activity to our collective research responsibilities),
here are some principles to guide our decisions and activity on what documents
get created:

1. **All are welcome to contribute**: There should be no or little barrier to
contributing to the documents and their content, aside from barriers due to
technology and skill in its use. If someone has the motivation and desire to
contribute, they should be able to do so fairly easily.

2. **Inclusion and participation in community through active contribution**:
Individuals who want to participate should actively contribute through not just
attending meetings, but also in creating, modifying, organizing, editing, and/or
developing the content on the website. Those who actively contribute should be
included in the community and encouraged to participate. 

3. **Content is dictated by direct and active contribution**: What gets created
or developed should be done by whoever contributes to creating or building it.
If someone wants or requests something to be created or modified, they are
encouraged and given the power to do so themselves. 
In combination with the first principle, the barrier to contributing is only 
dependent on learning the basic technical and writing skills rather than
any administrative barrier such as "requiring permission". If you want something,
than you are free to make it! We create and add content to the website based on
what we personally want or are motivated to do, rather than what we are told to
do^[...though we recognize that sometimes we must do things we are told to do.].

4. **Important or significant decisions are based on community consensus**:
Decisions should not or need not be blocked by requiring permission from
anything external to the community. This ensures things move forward as
continuously and unrestricted as possible. Important or significant decisions
could include things like approving and finalizing a document or deciding on
major infrastructural changes (e.g. platform to use for creating and managing
the content).

# Governance

# Navigating the GitHub project

The below video is a quick tutorial on how to navigate this project
on GitHub.

```{r video-tutorial-1}
embed_youtube("GoT_7DRRatw", height = 400) %>% 
    use_bs_responsive() %>% 
    use_align("center")
```

There are some terms used in the video:

- **Repository**: A [repository] is everything that is contained within
the project. In this case, the repository is the website with the 
[Issues], files, and subfolders for this project.
- **Issue**: An [Issue] is a task or to-do item that needs to be
completed. These to-do items can be assigned to people and can be
checked off as being done ("Closed").
- **Branch**: A [branch] is a separate, parallel set of files and
folders related to the project. In this project there is the "main"
branch that only the admin can edit. In order to add content
to the main branch, you need to create your own branch and create a
[Pull Request] of your changes and additions that you want added to
the main files. Branches and Pull Requests are heavily used in the
"[GitHub workflow]" that this project (and many many others) use.
More details about this are in the next section and video. Branches are
in some ways like separate files that you would email between other
contributors, but instead of everyone having different versions of the
file, here they are all contained in the same place (in the repository).
- **Pull Request**: A [Pull Request] is a request to add changes
you've made to files in your branch and have them put into the main
branch. When you make a Pull Request, it allows others to review what
you've changed and make comments on it. Think of it like "Track changes"
and the "Add comment" features of Word.

[Pull Request]: https://docs.github.com/en/github/collaborating-with-issues-and-pull-requests/about-pull-requests
[GitHub workflow]: https://guides.github.com/introduction/flow/
[Issue]: https://guides.github.com/features/issues/
[repository]: https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/about-repositories
[branch]: https://docs.github.com/en/github/getting-started-with-github/github-glossary#branch

# Adding new or modifying content as a team member

```{r video-tutorial-2, eval=FALSE}
embed_youtube("", height = 400) %>% 
    use_bs_responsive() %>% 
    use_align("center")
```

# Modifying existing content




