---
title: "Contributing guidelines"
description: |
  Guidelines for contributing to the documents.
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(vembedr)
```

This document contains instructions for how to contribute to developing these
documents. The content on this repository and website are licensed under the 
[CC-BY 4.0 License](https://github.com/steno-aarhus/research/blob/main/LICENSE.md), 
and by contributing content any contributors agree to these terms. We also
have a [Code of Conduct](https://steno-aarhus.github.io/research/CONDUCT.html)
that contributors agree to abide by.

# Guiding principles

In order to ensure that we get the most from creating these documents and that
we don't spend more time on this than is necessary (given it is largely a
secondary task and activity to our collective research responsibilities),
here are some principles to guide our decisions and activity on what documents
get created:

1. **All are welcome to contribute**: There should be no or little barrier to
contributing to the documents and their content, aside from barriers due to
technology and skill in its use. If someone has the motivation and desire to
contribute, they should be able to do so fairly easily.

2. **Inclusion and participation in community through active contribution**:
Individuals who want to participate should actively contribute through not just
attending meetings, but also in creating, modifying, organizing, editing, and/or
developing the content on the website. Those who actively contribute should be
included in the community and encouraged to participate. 

3. **Content is dictated by direct and active contribution**: What gets created
or developed should be done by whoever contributes to creating or building it.
If someone wants or requests something to be created or modified, they are
encouraged and given the power to do so themselves. 
In combination with the first principle, the barrier to contributing is only 
dependent on learning the basic technical and writing skills rather than
any administrative barrier such as "requiring permission". If you want something,
than you are free to make it! We create and add content to the website based on
what we personally want or are motivated to do, rather than what we are told to
do^[...though we recognize that sometimes we must do things we are told to do.].

4. **Important or significant decisions are based on community consensus**:
Decisions should not or need not be blocked by requiring permission from
anything external to the community. This ensures things move forward as
continuously and unrestricted as possible. Important or significant decisions
could include things like approving and finalizing a document or deciding on
major infrastructural changes (e.g. platform to use for creating and managing
the content).

# Governance

# Navigating the GitHub project

The below video is a quick tutorial on how to navigate this project
on GitHub.

```{r video-tutorial-1}
embed_youtube("GoT_7DRRatw", height = 400) %>% 
    use_bs_responsive() %>% 
    use_align("center")
```

There are some terms used in the video:

- **Repository**: A [repository] is everything that is contained within
the project. In this case, the repository is the website with the 
[Issues], files, and subfolders for this project.
- **Issue**: An [Issue] is a task or to-do item that needs to be
completed. These to-do items can be assigned to people and can be
checked off as being done ("Closed").
- **Branch**: A [branch] is a separate, parallel set of files and
folders related to the project. In this project there is the "main"
branch that only the admin can edit. In order to add content
to the main branch, you need to create your own branch and create a
[pull request] of your changes and additions that you want added to
the main files. Branches and pull requests are heavily used in the
"[GitHub workflow]" that this project (and many many others) use.
More details about this are in the next section and video. Branches are
in some ways like separate files that you would email between other
contributors, but instead of everyone having different versions of the
file, here they are all contained in the same place (in the repository).
- **Pull request**: A [pull request] is a request to add changes
you've made to files in your branch and have them put into the main
branch. When you make a pull request, it allows others to review what
you've changed and make comments on it. Think of it like "Track changes"
and the "Add comment" features of Word.

[pull request]: https://docs.github.com/en/github/collaborating-with-issues-and-pull-requests/about-pull-requests
[GitHub workflow]: https://guides.github.com/introduction/flow/
[Issue]: https://guides.github.com/features/issues/
[repository]: https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/about-repositories
[branch]: https://docs.github.com/en/github/getting-started-with-github/github-glossary#branch

# Adding new or modifying content as a team member

The video below is a tutorial on how to add or modify content and files
on the GitHub project. For this to work, you need to be added as a team
member and have a GitHub Account. Make sure to send the admin (Luke Johnston)
your GitHub username so he can add you.

```{r video-tutorial-2}
embed_youtube("Z1G4rBX3tXM", height = 400) %>% 
    use_bs_responsive() %>% 
    use_align("center")
```

Content is formatted using Markdown (in this case, R Markdown) and you
can learn how to write in Markdown on the 
[GitHub Markdown Guide](https://guides.github.com/features/mastering-markdown/).
There are also some terms used in the video:

- **Commit**: A commit is the set of changes you've made to a file that
will be put into the history. In general, committing changes to the
history is better done often.
- **Changes/commit History**: The commit history is all the changes,
either additions or deletions, that have been done to the files in the
project.

Here is a written description of the workflow to adding or modifying
text in the files:

1. Create or switch to your own branch.
2. Either use the "Add a file" button or choose a file and click the
"Edit this file" button.
3. Add Markdown formatted text to the file.
4. Scroll to the bottom to the "Commit" changes section and write
a *short, brief* commit message about what you changed and why (can be optional).
Then, making sure you have your branch selected, click the Commit button.
    - Commit your changes often. Don't be shy about making many commits
    to the files you are changing.
5. When you are happy with your changes and want them to be added to 
the main branch (so they can be put on the website), click the "pull
request" button, write a short message as a title on what you are
changing or adding in the pull request, and click "Create pull request".
Now your changes can be reviewed!

## The basics of writing in Markdown

The video below is a tutorial on the basics of using Markdown to write the content
of this website. When you write content for any documents on this repository,
the content needs to be written in Markdown. So take some time to watch the
video and learn a bit about Markdown. I promise, it won't take long to learn!

```{r video-tutorial-markdown}
embed_youtube("_ovKJek9-Rk", height = 400) %>% 
    use_bs_responsive() %>% 
    use_align("center")
```

For more guides and references on writing in Markdown, see GitHub's Guide
[*Mastering Markdown*](https://guides.github.com/features/mastering-markdown/)
or, for a more reference and list style of documentation, GitHub's 
[*Writing on GitHub*](https://docs.github.com/en/github/writing-on-github/basic-writing-and-formatting-syntax)
documentation. To see a "real-world" example, check out how the Code of Conduct
is [written](https://github.com/steno-aarhus/research/blob/main/CONDUCT.Rmd).

<!-- ## Using RStudio to contribute -->

```{r, eval=FALSE, echo=FALSE}
# Make sure usethis and distill packages are installed
install.packages(c("usethis", "distill"))
# Download the new project to your Desktop
usethis::create_from_github("steno-aarhus/research")
# Open
distill::create_post("", "")
```

